A fast algorithm for computing best response strategies in two-person sequential games

### 2014-07-26 paper.tex
'running average ||e - Exk||_2' stopping criterion

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\
\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
$\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
$i_C$: \quad \textit{the indicator function of the convex set $C$}\\
$\Pi_C$: \quad \textit{the euclidean projector onto the convex set $C$}\\
$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
$\|K\|_2$: \quad \textit{the matrix 2-norm of the matrix $K$}\\
$f^*$: \quad \textit{the Fenchel transform of the convex l.s.c function $f$}\\
$E^{-1}(U)$: \quad \textit{the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}

@@

Now, let's observe that $i_{E^{-1}(\{e\})}(x) = \underset{\zeta \in \mathbb{R}^p}{max}\text{ }\zeta^T(e - Ex)$, and so one can re-write (2) as:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \zeta \in \mathbb{R}^p}{max}\text{ }
  \begin{bmatrix}y\\\zeta\end{bmatrix}^TKx + G(x) - F^*(y, \zeta)
  \label{eq:pd_opt}
\end{equation}
where we've defined:
\begin{equation}
  \left.
  \begin{aligned}
    K := -\begin{bmatrix}A\\E\end{bmatrix}\\
    G := g - i_{E^{-1}(\{b\})} = i_{\mathbb{R}_{+}^n}\\
    F^*: (y, \zeta) \mapsto (f^*(y) - \zeta^Te) = (i_{\{y_0\}}(y) - \zeta^Te)
  \end{aligned}
  \right\}
\end{equation}

@@

\begin{algorithm}[htb]
\caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
\textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
\textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
\Repeat{
  convergence}{
  \begin{eqnarray*}
    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
    x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
    \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
    k &\leftarrow& k + 1
  \end{eqnarray*}
} \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
\label{Tab:pseudocode_pb}
\end{algorithm}

\subsection{Convergence of the algorithm and practical stopping-criteria}
Pending...

>>>>

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\\\
$a^Tb$: \quad \textit{the dot product of two vectors $a$ and $b$}\\
$\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
$i_C$: \quad \textit{the indicator function of the convex set $C$}\\
$\Pi_C$: \quad \textit{the euclidean projector onto the convex set $C$}\\
$\|K\|_2$: \quad \textit{the matrix 2-norm of the matrix $K$}\\
$f^*$: \quad \textit{the Fenchel transform of the convex l.s.c function $f$}\\
\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
$E^{-1}(U)$: \quad \textit{the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}

@@

Now, let's observe that $i_{E^{-1}(\{e\})}(x) = \underset{\zeta \in \mathbb{R}^p}{max}\text{ }\zeta^T(e - Ex)$, and so one can re-write (2) as:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \zeta \in \mathbb{R}^p}{max}\text{ }
  \begin{bmatrix}y\\\zeta\end{bmatrix}^TKx + G(x) - F^*(y, \zeta)
  \label{eq:pd_opt}
\end{equation}
where we've defined:
\begin{equation}
  \left.
  \begin{aligned}
    K := -\begin{bmatrix}A\\E\end{bmatrix}\\
    G := g - i_{E^{-1}(\{b\})} = i_{\mathbb{R}_{+}^n}\\
    F^*: (y, \zeta) \mapsto (f^*(y) - \zeta^Te) = (i_{\{y_0\}}(y) - e^T\zeta)
  \end{aligned}
  \right\}
\end{equation}

@@

\begin{remark}
The derivation above reveals that in equation \eqref{eq:opt_pb} above, if the constraint ``$x \ge 0$'' is replaced by
a constraint ``$x \in C$'' (thus obtaining a new problem) where $C$ is a convex set
%% onto which euclidean projections
%% can be easily computed (for example, a probability simplex)
, then we simply need to replace the operator ``$(.)_+$''
with ``$\Pi_C$'' in the equations to obtain a corresponding algorithm. Of course, this is because $i_C^* = \Pi_C$.
\end{remark}

\begin{algorithm}[htb]
\caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
\textbf{Let} $\epsilon > 0$ be a given tolerance.\\
\textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
\textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
\Repeat{
  $\frac{1}{k + 1}\sum_{j=0}^{k}{\|e - E\tilde{x}^{(j)}\|^2_2} < \epsilon$}{
  \begin{eqnarray*}
    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
    x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
    \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
    k &\leftarrow& k + 1
  \end{eqnarray*}
} \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
\label{Tab:pseudocode_pb}
\end{algorithm}

\subsection{Convergence analysis of the algorithm}
Pending...
